Future challenges for Research Software Engineering

### 2025-05-18 future_challenges_for_RSEng.tex
add our ideas what using AI tools in future might look like

>>>>

The lessons learned from Human Factors research of the previous decades \cite{Simkute2025} applied to AI tools helped resolve the initial issues outlined above.
We envision that AI will be transforming research processes by enabling rapid analysis of massive datasets, uncovering patterns and insights that would have been impossible or prohibitively time-consuming for humans alone to find.
In research and development, AI will accelerate scientific breakthroughs in fields like healthcare, climate science, and materials engineering by automating complex modelling and predictive tasks.
